### 2014-11-05 related.tex
edits

Operation-based RDTs have been widely studied in terms of their algorithmic
properties~\cite{SSS,Burckhardt2014}, and several systems utilize this model to
construct distributed data structures~\cite{Cassandra,Bayou,Tango}. These
systems typically propose to implement the datatypes directly over a cluster of
nodes, and only focus on basic eventual consistency. Hence, these systems
implement custom solutions for durability and fault-tolerance. \name realizes
RDTs stronger consistency models on top of off-the-shelf eventually consistent
distributed stores. In this respect, \name is similar to~\cite{BoltOn} where
causal consistency is achieved through a shim layer on Cassandra, which
explicitly tracks and enforces depedencies between updates.
However,~\cite{BoltOn} does not support user-defined RDTs, automatic contract
classification and transactions.

@@

Our contract language is inspired by the axiomatic decription of RDT semantics
proposed by~\cite{Burckhardt2014}. While they use axioms for formal
verification of correctness of an RDT implementation, we utilize them as a
means for the user to express the desired consistency guarantees in the
application. Similar to their work, our contract language does not incorporate
real (i.e., wall-clock) time. Hence, it cannot describe store semantics such as
recency or bounded-staleness guarantees offered by certain
stores~\cite{Pileus}.

>>>>

Operation-based RDTs have been widely studied in terms of their algorithmic
properties~\cite{SSS,Burckhardt2014}, and several systems utilize this model to
construct distributed data structures~\cite{Cassandra,Bayou,Tango}. These
systems typically propose to implement the datatypes directly over a cluster of
nodes, and only focus on basic eventual consistency. Hence, these systems
implement custom solutions for durability and fault-tolerance. \name realizes
RDTs stronger consistency models on top of off-the-shelf eventually consistent
distributed stores. In this respect, \name is similar to~\cite{BoltOn} where
causal consistency is achieved through a shim layer on Cassandra, which
explicitly tracks and enforces dependencies between updates.
However,~\cite{BoltOn} does not support user-defined RDTs, automatic contract
classification and transactions.

@@

Our contract language is inspired by the axiomatic description of RDT semantics
proposed by~\cite{Burckhardt2014}. While they use axioms for formal
verification of correctness of an RDT implementation, we utilize them as a
means for the user to express the desired consistency guarantees in the
application. Similar to their work, our contract language does not incorporate
real (i.e., wall-clock) time. Hence, it cannot describe store semantics such as
recency or bounded-staleness guarantees offered by certain
stores~\cite{Pileus}.
